A contrast of meta and metafor packages for meta-analyses in R

### 2020-03-30 ms/2020/contrastRmd.Rmd
contrast table added

\newpage
### Table 1.  
A contrast of meta and metafor using

>>>>

\newpage
### Table 1.  
A contrast of meta and metafor using the critical principles developed in 'A checklist for choosing between R packages in ecology and evolution' [@RN6507].

```{r table1, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(kableExtra)

table1 <- read_csv("table1.csv")
knitr::kable(table1, "latex", booktabs = TRUE, longtable = TRUE) %>%
  column_spec(1, width = "1cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "5cm") %>%
  column_spec(4, width = "5cm") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
